\section{Matrices}
\subsection{Creating a matrix}
Matrices can be created using the \texttt{matrix()} command. The arguments to be supplied are 
\begin{enumerate}
\item vector of values to be entered
\item Dimensions of the matrix, specifying either the numbers of rows or columns.
\end{itemize}
%-------------------------------------------------------------------------%
Additionally you can specify if the values are to be allocated by row or column. By default they are allocated by column.
\begin{verbatim}
Vec1=c(1,4,5,6,4,5,5,7,9)		# 9 elements
A=matrix(Vec,nrow=3)		#3 by 3 matrix. Values assigned by column.
A
B= matrix(c(1,6,7,0.6,0.5,0.3,1,2,1),ncol=3,byrow =TRUE)
B				          #3 by 3 matrix. Values assigned by row.
\end{verbatim}	
If you have assigned values by column, but require that they are assigned by row, you can use the transpose function
\begin{verbatim}
t().
t(A)				# Transpose
A=t(A)	
\end{verbatim}

Another methods of creating a matrix is to "bind" a number of vectors together, either by row or by column. The commands are rbind() and cbind() respectively.
\begin{verbatim}
x1 =c(1,2) ; x2 = c(3,6)
rbind(x1,x2)
cbind(x1,x2)
\end{verbatim}




Particular rows and columns can be accessed by specifying the row number or column number, leaving the other value blank.
\begin{verbatim}
A[1,]	  # access first row of A
B[,2]   # access first column of B
\end{verbatim}
Addition and subtractions
For matrices, addition and subtraction works on an element- wise basis. The first elements of the respective matrices are added, and so on.
A+B
A-B

%-------------------------------------------------------------------------------%
\subsection{Matrix Multiplication}
To multiply matrices, we require a special operator for matrices; "%*%".
If we just used the normal multiplication, we would get an element-wise multiplication.
\begin{framed}
\begin{verbatim}
A * B  		#Element-wise multiplication
A %*% B  	#Matrix multiplication
\end{verbatim}
\end{framed}
We can compute crossproducts using the \texttt{crossprod()} command. If only one matrix is used it
\begin{framed}
\begin{verbatim}
crossprod(A,B) 		# A'B
crossprod(A) 			# A'A
Diagonals
\end{verbatim}
\end{framed}
The \texttt{diag()} command is a very versatile function for using matrices.
It can be used to create a diagonal matrix with elements of a vector in the principal diagonal. For an existing matrix, it can be used to return a vector containing the elements of the principal diagonal.


Most importantly, if k is a scalar,  \texttt{diag()}  will create a $k \times k$ identity matrix.
\begin{framed}
\begin{verbatim}
Vec2=c(1,2,3)
diag(Vec2)	#	Constructs a diagonal matrix based on values of Vec2
diag(A)	#        Returns diagonal elements of A as a vector
diag(3)	#	creates a 3 x 3 identity matrix
diag(diag(A)) #  	Diagonal matrix D of matrix A (Jacobi Method)
\end{verbatim}
\end{framed}
\subsection{Determinants, Inverse Matrices and solving Linear systems}
To compute the determinant of a square matrix, we simply use the \texttt{det()} command
\begin{framed}
\begin{verbatim}
det(A)
det(B)
\end{verbatim}
\end{framed}
To find the inverse of a square matrix, we use the solve() command, specifying only the matrix in question
solve(A)

To solve a system of linear equations in the form Ax=b , where A is a square matrix, and b is a column vector of known values, we use the solve() command to determine the values of the unknown vector x.
b=vec2  # from before
solve(A, b)
Row and Column Statistics.
Statistic on the rows and columns can easily be computed if required.
\begin{framed}
\begin{verbatim}
rowMeans(A)  # Returns vector of row means.
rowSums(A)  # Returns vector of row sums.
colMeans(A)  # Returns vector of column means.
colSums(A)  # Returns vector of coumn means.
\end{verbatim}
\end{framed}

%-------------------------------------------------------------------------------%
\subsection{Eigenvalues and Eigenvectors}
The eigenvalues and eigenvectors can be computed using the \texttt{eigen()} function.  A data object is created.
This is a very important type of matrix analysis, and many will encounter it again in future modules.
\begin{framed}
\begin{verbatim}
Y = eigen(A)
names(Y)
"	y$val are the eigenvalues of A
"	y$vec are the eigenvectors of A

\end{verbatim}
\end{framed}
%-------------------------------------------------------------------------------%
Part 2 Revision on Earlier Material
"	Accessing a column of a data frame
"	Accessing a row of a data frame

A particular row can be accessed by specifying the row index , while leaving the column index empty

Info [4,]			# Fourth row of "Info" is called

A sequence of rows can be accessed by specifying a sequence of rows as follows.

Info [10:15,]		# tenth row to fifteenth row of "Info" is called
